Directionality and Direction of Innovation in the Swedish Forest-Based Bioeconomy Transition

### 2024-03-14 paper.qmd
fix migration issues to mac

# full code labels for merging

codes_df = pd.read_sql("SELECT * FROM classification_codes", conn)

codes_df["Category"] = codes_df["Category"].str.strip()
uncertain_eco = {"Code": "000", "Category": "Unsure"}
codes_df = codes_df.append(uncertain_eco, ignore_index=True)

>>>>

# full code labels for merging
codes_df = pd.read_sql("SELECT * FROM classification_codes", conn)

codes_df["Category"] = codes_df["Category"].str.strip()
uncertain_eco = {"Code": ["000"], "Category": ["Unsure"]}
codes_df = pd.concat([codes_df, pd.DataFrame(uncertain_eco)], ignore_index=True)
